\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-07 paper.qmd
Added intro section for Five Gausssian cluster example

In this section, we will assess how t-SNE, UMAP, and PaCMAP algorithms preserve the clustering structure. We will use a simulated dataset consisting of five spherical Gaussian clusters where each cluster occupies a different corner of the $4\text{-}D$ space, with each cluster containing an equal number of points ($1000$) and the same within-cluster variation. The data simulated from $\Sigma = \begin{pmatrix}
0.0025 & 0 & 0 & 0 \\
0 & 0.0025 & 0 & 0 \\
0 & 0 & 0.0025 & 0 \\
0 & 0 & 0 & 0.0025 \\
\end{pmatrix}$.

>>>>

In this section, the evaluation focuses on how effectively the tSNE, UMAP, and PaCMAP algorithms preserve the clustering structure. The data consists of five $4\text{-}D$ clusters, each with $1000$ points generated from a multivariate normal distribution with a small variance of 0.0025. The first cluster is centered at $(0, 0, 0, 0)$, the second at $(1, 0, 0, 0)$, the third at $(0, 1, 0, 0)$, the fourth at $(0, 0, 1, 0)$, and the fifth at $(0, 0, 0, 1)$.

<!-- In this section, we will assess how tSNE, UMAP, and PaCMAP algorithms preserve the clustering structure. We use a simulated dataset consisting of five spherical Gaussian clusters where each cluster occupies a different corner of the $4\text{-}D$ space, with each cluster containing an equal number of points ($1000$) and the same within-cluster variation. The data simulated from $\Sigma = \begin{pmatrix} -->
<!-- 0.0025 & 0 & 0 & 0 \\ -->
<!-- 0 & 0.0025 & 0 & 0 \\ -->
<!-- 0 & 0 & 0.0025 & 0 \\ -->
<!-- 0 & 0 & 0 & 0.0025 \\ -->
<!-- \end{pmatrix}$. -->

### 2024-09-07 paper.tex
Added intro section for Five Gausssian cluster example

In this section, we will assess how t-SNE, UMAP, and PaCMAP algorithms
preserve the clustering structure. We will use a simulated dataset
consisting of five spherical Gaussian clusters where each cluster
occupies a different corner of the \(4\text{-}D\) space, with each
cluster containing an equal number of points (\(1000\)) and the same
within-cluster variation. The data simulated from
\(\Sigma = \begin{pmatrix}
0.0025 & 0 & 0 & 0 \\
0 & 0.0025 & 0 & 0 \\
0 & 0 & 0.0025 & 0 \\
0 & 0 & 0 & 0.0025 \\
\end{pmatrix}\).

>>>>

In this section, the evaluation focuses on how effectively the tSNE,
UMAP, and PaCMAP algorithms preserve the clustering structure. The data
consists of five \(4\text{-}D\) clusters, each with \(1000\) points
generated from a multivariate normal distribution with a small variance
of 0.0025. The first cluster is centered at \((0, 0, 0, 0)\), the second
at \((1, 0, 0, 0)\), the third at \((0, 1, 0, 0)\), the fourth at
\((0, 0, 1, 0)\), and the fifth at \((0, 0, 0, 1)\).
